Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-09 2019/NUMTA_Barkalov/Special Issure/article.tex
Added left alignment in formulas.
Merged the bibliography

\begin{eqnarray}
	R(i) = \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{z_i+z_{i-1}-2z_M^*}{r_M\mu_M} \geq \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\mu_M\Delta_i}{r_M\mu_M} \nonumber \\
	\geq \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\Delta_i}{r_M} = \Delta_i + \Delta_i\frac{(z_i-z_{i-1})^2/\Delta_i^2}{r_M^2\mu_M^2\Delta_i^2} - 2\frac{\Delta_i}{r_M}
\nonumber \\
	\geq \Delta_i + \frac{\Delta_i}{r_M^2} - 2\frac{\Delta_i}{r_M} = \Delta_i \left( 1-\frac{1}{r_M} \right)^2>0
	\nonumber
\end{eqnarray}

@@

\begin{eqnarray}
	g_1(y_1, y_2)= 0.01 \left( (y_1-2.2)^2+(y_2-1.2)^2-2.25 \right) \leq 0, \nonumber \\
	g_2(y_1, y_2)= 100 \left(1-(y_1-2)^2/1.44+(0.5y_2)^2 \right) \leq 0, \nonumber \\
	g_3(y_1, y_2)= 10 \left( y_2 - 1.5 - 1.5 \sin{\left( 6.283(y_1-1.75) \right)}\right) \leq 0
	\nonumber
\end{eqnarray}

@@

\begin{eqnarray}
	R(j) = \Delta_i + \frac{(z_j-z_{j-1})^2}{r_{\nu}^2\mu_{\nu}^2\Delta_i} - 2\frac{z_j+z_{j-1}-2z_{\nu}^*}{r_{\nu}\mu_{\nu}} \geq \nonumber \\
	\Delta_i + 4\frac{z_{\nu}^*-\left( g_{\nu}\left( y(\bar x) \right)+L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)\right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	=\Delta_i-4\frac{L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	=\Delta_i-4\frac{L_{\nu}\sqrt{N+3}\left( \alpha^{\frac{1}{N}}+(1-\alpha)^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	\geq \Delta_i\left(1-4\frac{L_{\nu}\sqrt{N+3}\max_{0\leq\alpha\leq1} {\left( \alpha^{\frac{1}{N}}+(1-\alpha)^{\frac{1}{N}} \right)}}{r_{\nu}\mu_{\nu}} \right)+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	= \Delta_i\left(1-4\frac{2^{3-1/N}L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right)+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \geq 0
	\nonumber
\end{eqnarray}

\begin{eqnarray}
	R(j) = 2\Delta_i - 4\frac{z_j-z_{\nu}^*}{r_{\nu}\mu_{\nu}} \geq 2\Delta_i+4\frac{z_{\nu}^*-\left( g_{\nu}\left(y(\bar x)\right)+2L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	= 2\Delta_i - 8\frac{L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}}}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	\geq 2\Delta_i\left( 1-4\frac{L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right) + 4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} > 0
	\nonumber
\end{eqnarray}

@@

\cite{Evtushenko, Piyavskii1972, Shubert1972, Evtushenko2009, Evtushenko2013, Strongin2000, Sergeyev2013, Pinter1996, Jones2009, Wood1991, Meewella1988, Mladineo1986, Vaz2009, Stripinis2019, Paulavicius2016, Pillo2012, Pillo2016, Barkalov2017_1, Barkalov2017_2, Sergeyev2006, Zilinskas2008, Sovrasov2019}.

\section*{References}

>>>>

\begin{eqnarray}
	R(i) & = & \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{z_i+z_{i-1}-2z_M^*}{r_M\mu_M} \geq \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\mu_M\Delta_i}{r_M\mu_M} \nonumber \\
	& \geq & \Delta_i + \frac{(z_i-z_{i-1})^2}{r_M^2\mu_M^2\Delta_i} - 2\frac{\Delta_i}{r_M} = \Delta_i + \Delta_i\frac{(z_i-z_{i-1})^2/\Delta_i^2}{r_M^2\mu_M^2\Delta_i^2} - 2\frac{\Delta_i}{r_M}
\nonumber \\
	& \geq & \Delta_i + \frac{\Delta_i}{r_M^2} - 2\frac{\Delta_i}{r_M} = \Delta_i \left( 1-\frac{1}{r_M} \right)^2>0  
	\nonumber
\end{eqnarray}

@@

\begin{eqnarray}
	g_1(y_1, y_2) &=& 0.01 \left( (y_1-2.2)^2+(y_2-1.2)^2-2.25 \right) \leq 0, \nonumber \\
	g_2(y_1, y_2) &=& 100 \left(1-(y_1-2)^2/1.44+(0.5y_2)^2 \right) \leq 0, \nonumber \\
	g_3(y_1, y_2) &=& 10 \left( y_2 - 1.5 - 1.5 \sin{\left( 6.283(y_1-1.75) \right)}\right) \leq 0
	\nonumber
\end{eqnarray}

@@

\begin{eqnarray}
	R(j) &=& \Delta_i + \frac{(z_j-z_{j-1})^2}{r_{\nu}^2\mu_{\nu}^2\Delta_i} - 2\frac{z_j+z_{j-1}-2z_{\nu}^*}{r_{\nu}\mu_{\nu}}  \nonumber \\
	&\geq& \Delta_i + 4\frac{z_{\nu}^*-\left( g_{\nu}\left( y(\bar x) \right)+L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)\right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	&=& \Delta_i-4\frac{L_{\nu}\sqrt{N+3}\left( (x_j-\bar x)^{\frac{1}{N}}+(\bar x - x_{j-1})^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	&=& \Delta_i-4\frac{L_{\nu}\sqrt{N+3}\left( \alpha^{\frac{1}{N}}+(1-\alpha)^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	&\geq& \Delta_i\left(1-4\frac{L_{\nu}\sqrt{N+3}\max_{0\leq\alpha\leq1} {\left( \alpha^{\frac{1}{N}}+(1-\alpha)^{\frac{1}{N}} \right)}}{r_{\nu}\mu_{\nu}} \right)+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	&=& \Delta_i\left(1-4\frac{2^{3-1/N}L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right)+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \geq 0
	\nonumber
\end{eqnarray}

\begin{eqnarray}
	R(j) &=& 2\Delta_i - 4\frac{z_j-z_{\nu}^*}{r_{\nu}\mu_{\nu}} \geq 2\Delta_i+4\frac{z_{\nu}^*-\left( g_{\nu}\left(y(\bar x)\right)+2L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}} \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	&=& 2\Delta_i - 8\frac{L_{\nu}\sqrt{N+3}(x_j-\bar x)^{\frac{1}{N}}}{r_{\nu}\mu_{\nu}}+4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} \nonumber \\
	&\geq& 2\Delta_i\left( 1-4\frac{L_{\nu}\sqrt{N+3}}{r_{\nu}\mu_{\nu}} \right) + 4\frac{z_{\nu}^*-g_{\nu}\left( y(\bar x) \right)}{r_{\nu}\mu_{\nu}} > 0
	\nonumber
\end{eqnarray}

@@

\cite{Evtushenko1971, Piyavskii1972, Shubert1972, Evtushenko2009, Evtushenko2013, Strongin2000, Sergeyev2013, Pinter1996, Jones2009, Wood1991, Meewella1988, Mladineo1986, Vaz2009, Stripinis2019, Paulavicius2016, Pillo2012, Pillo2016, Barkalov2017_1, Barkalov2017_2, Sergeyev2006, Zilinskas2008, Sovrasov2019}.
